### 2024-03-15 sections/1stratified.tex
a few things in §2 (ongoing)

\begin{remark}
    Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence. For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ constrols framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms. On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[Proposition 018F]{lurie_kerodon}, \cite{joyal}). Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full sub-$\infty$-category is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well. In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism. However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Spaces}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures. By unstraightening, this determines a right fibration for which, by abuse, we write $\mathsf{D}^G_n=\mathsf{B}G\to \mathsf{D}_n\hookrightarrow\bsc$.
\end{remark}

>>>>

\begin{remark}
    Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence. For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ constrols framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms. On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[Corollary 018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[Proposition 018F]{lurie_kerodon}, \cite{joyal}). Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full sub-$\infty$-category is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well. In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism. However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Spaces}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures. By unstraightening, this determines a right fibration for which, by abuse, we write $\mathsf{D}^G_n=\mathsf{B}G\to \mathsf{D}_n\hookrightarrow\bsc$.
\end{remark}

### 2024-03-15 sections/2homology.tex
a few things in §2 (ongoing)

Factorization homology (also known as topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
%
\begin{equation}
    \int_{M} A \in \catC.
\end{equation}
%
In fact this is only the simplest variant of factorization homology. Variants that accommodate stratified manifolds instead of smooth ones and even $(\infty,n)$-categories instead of algebras have also been worked out. Given the focus of the present work, we will be concerned with the variant that can evaluate stratified manifolds. We will not be interested, however, in generalizing the algebraic input beyond disk algebras to the realm of $(\infty,n)$-categories. Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense, and giving the name. The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}. Later, in \cref{thm:disk_alg=lcfa}, we will also see how factorization homology serves to construct factorization algebras. The theory of factorization homology has been deeply developed in \cite{af_fhtop, aft_fhstrat}, especially in the manner that we introduce it in here. A good introduction, is thus, given by \cite{af_primer}, which we will be following.

In the following, and from now on, we let $\catC$ be a symmetric monoidal $\infty$-category that is \emph{$\otimes$-presentable} \cite{af_fhtop}, i.e. it satisfies:
%
\begin{enumerate}
    \item $\catC$ is presentable: it admits colimits, and every object is a filtered colimit of compact objects\footnote{For the exact meaning of these terms we refer the reader to \cite[sec.5.3]{lurie_htt}. For us, it will suffice to give examples of $\infty$-categories that satisfy these requirements.}, and
    \item the monoidal structure distributes over colimits: for all $c \in \catC$, the functor $c \otimes -: \catC \xrightarrow{} \catC$ takes colimit diagrams to colimit diagrams.
\end{enumerate}

@@

\begin{example}
    The following are examples of $\otimes$-presentable categories:
    %
    \begin{enumerate}
        \item chain complexes $\mathscr{C}\mathsf{h}_{\mathbb{k}}$ over a commutative ring $\mathbb{k}$, where equivalences are given by quasi-isomorphism. The symmetric monoidal structure can be both direct sum $\oplus$ or tensor product $\otimes$.
        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Spaces}$ or $\cat$).
    \end{enumerate}
    %
    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most useful for the purposes of mathematical physics, which is why it's the choice for the development in \cite{cg2016} and \cite{ginot2015}.
\end{example}

@@

@@

\begin{remark}
    The exact specification of the above $\infty$-category is not immediate, but the explanations given in \cite[def.2.0.0.7]{lurie_ha}, \cite[rem.2.1.2.19]{lurie_ha} and \cite[def.2.1.3.7]{lurie_ha} clarify the matter. A succinct explanation is also given around \cite[def.1.11]{aft_fhstrat}. Informally, the objects will be symmetric monoidal functors from $\disk(\bstr)$ to $\catC$. These are given by functors $F:\disk(\bstr) \xrightarrow{} \catC$ together with maps
    %
    \begin{equation}\label{eq:symmon_maps}
        F(U \sqcup V) \xrightarrow{\ \ \simeq \ \ } F(U) \otimes F(V),
    \end{equation}
    %
    and such that the swap in $\disk(\bstr)$, $U \sqcup V \simeq V \sqcup U$, is sent to the swap in $\catC$, $F(U) \otimes F(V) \simeq F(V) \otimes F(U)$, in a way that is compatible with the maps in \cref{eq:symmon_maps}. A good informal explanation of this and other topics related to disk algebras can be found in the lecture notes \cite{tanaka20}.
\end{remark}

@@

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[sec.5.1]{lurie_ha}. %or alternatively in appendix \cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent. Through the work of \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
\end{remark}

@@

\begin{remark}
    Because of \cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the constructible bundle $f$.
\end{remark}

@@

The upshot is that, with our setup and assumptions on $\catC$, the guess that the value of factorization homology can be calculated by a colimit is correct and given by the standard expressions for left Kan extensions
%
\begin{equation}
    \int_M A \simeq \mathsf{colim} \left(\disk(\bstr)_{/M} \xrightarrow{} \disk(\bstr) \xrightarrow{A} \catC \right)
\end{equation}
%
in the absolute case, and
%
\begin{equation}
    \int_{N \xhookrightarrow{} M} A \simeq \mathsf{colim} \left((\disk_{/M})_{/(N \xhookrightarrow{} M)} \xrightarrow{} \disk_{/M} \xrightarrow{A} \catC \right)
\end{equation}
%
in the relative case. Namely, the left Kan extension of underlying $\infty$-categories lifts to a symmetric monoidal, in the absolute case, and operadic, in the relative case, left Kan extension. In the relative case, we will almost always abuse notation and write $\int_N A$ instead of $\int_{N \xhookrightarrow{} M} A$, but because of \cref{lem:double_slice} this is not much of an abuse. Furthermore, factorization homology is also shown to be fully faithful due to this being true for the inclusion $\disk(\bstr) \xrightarrow{} \mfld(\bstr)$, as well as, the relative version with slices.

@@

We want to show that disk algebras with $\mathsf{D}_1^{\partial, *}$-structure, as defined in \cref{con:d_1^bor_structure}, can be described algebraically. For this we set up two $\infty$-operads $\mathsf{Assoc^{RL}}$ and $\mathsf{O^{RL}}$.

@@

\begin{remark}
    More informally, what the \cref{con:assocRL} says is that the only multi-morphism domains possible are $\emptyset$, $(A,A,\dots,A)$, $(R,A,\dots,A)$ or $(A,\dots,A, L)$ and that there is one multi-morphism for each permutation of the $A$ entries. This makes it clear that algebras over this $\infty$-operad will be unital, (homotopy) associative algebras, together with a unital left and a unital right module.
\end{remark}

@@

\begin{proposition}\label{prop:disk1bor_over_int=ORL}
    There are equivalences of $\infty$-operads
    %
    \begin{equation}
        \disk[r] (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \mathsf{O^{RL}} \quad
    \end{equation}
    %
    that descend to the equivalences of \cref{prop:disk1bor=assocRL}.
\end{proposition}

\begin{proof}
    As in the proof of \cref{prop:disk1bor=assocRL} the first equivalence is clear. The idea to keep in mind is that since the boundary of $[-1,1]$ consists of a left point and a right point, there can only be oriented embeddings of disks into $[-1,1]$ with at most one of each of $\left[-1,1 \right)$ and $\left( -1, 1 \right]$. These are then clearly the objects that map to the respective distinguished subsets. Observing the definition of $\mathsf{O^{RL}}$ clearly offers a bijection on morphism spaces since they are by definition order preserving maps, and the embeddings are oriented. It is trivial to check that these maps lie over $\mathsf{Fin}_*$ and that they send active morphisms to active morphisms completing the proof.
\end{proof}

@@

\begin{proof}
    The only thing to show is the middle equivalence. This follows from \cref{lem:disk/M_to_disk}, which we will introduce later. 
\end{proof}

\begin{remark}\label{rem:fin_equiv_natural}
    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
    %
    \begin{equation}\label{eq:fin_equivs_obj}
        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
    \end{equation}
    %
    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist. We remark here that these equivalences are actually even natural in $G$. To explain this, we first notice that the equivalences in \cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
    %
    \begin{equation}\label{eq:fin_equivs_cat}
        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
    \end{equation}
    %
    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one. Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the slice construction is functorial, which, after restricting, defines the functors
    %
    \begin{align}
        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
    \end{align}
    %
    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$. We can now state that by naturality in $G$ we mean that the functors of \cref{eq:fin_equivs_cat} assemble into an equivalence of functors   
    %
    \begin{equation}
        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
    \end{equation}
    %
    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
\end{remark}

@@

    Since the equivalences above come from an argument about finality, \cref{rem:fin_equiv_natural} tells us that they are actually even natural in the algebra variable $(R, A, L)$, so that the equivalence lifts to the level of functors.
\end{proof}

@@

The construction of \cref{lem:f^-1} gives a functor which allows us to change the stratified manifold over which we work. This brings about the important operation of pushforward:

@@

\begin{remark}\label{rem:fh_pushforward_functorial}
    As was the case with the bar construction the equivalence of \cref{thm:fh_pushforward}, comes about through an argument about a final functor, this means that, through \cref{rem:fin_equiv_natural} there is even an equivalence between functors
    %
    \begin{equation}
        \int_M -, \int_N f_* - : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \catC.
    \end{equation}
\end{remark}

@@

\begin{proof}
    The definition comes with a claim that the canonical morphism in $\catC$ exists. This we need to show. The data of a collar-gluing $f: M \xrightarrow{} [-1,1]$ allows us to pushforward $F$ to
    %
    \begin{equation}
        f_*F: \disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{f^{-1}} \mfld(\bstr)_{/M} \xrightarrow{} \mfld(\bstr) \xrightarrow{F} \catC.
    \end{equation}
    %
    By \cref{prop:disk1bor=assocRL} we know that this data defines an $\mathsf{Assoc^{RL}}$-algebra in $\catC$ whose right module, algebra and left module are exactly $F(M_-)$, $F(M_0 \times \mathbb{R})$ and $F(M_+)$. Further using \cref{prop:barconst=intinterval} we have
    %
    \begin{equation}
        F(M_-) \bigotimes\limits_{f(M_0 \times \mathbb{R})}  F(M_+)\simeq \int_{[-1,1]} f_* F \xrightarrow{\quad} F (f^{-1}[-1,1]) = F(M),
    \end{equation}
    %
    where the morphism is given by the fact that factorization homology is a colimit.
\end{proof}

@@

All of the above statements about factorization homology and disk algebras are quite general, and they do not say anything specific about a stratified structure, if there is one. Namely, had we stuck to smooth manifolds (possibly with boundary) we could have made similar statements. In this section we describe a result that clearly uses the stratified structure, and quantifies some additional information it can encode. It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \cref{def:framed_d_under_n_structure}. %We will, in a roundabout way, recover this result in \cref{ch:classif_defect_mfld}, but here we state it in the original form.

@@

\begin{remark}
    The above theorem is a slight generalization of, and heavily relies on, the proof of the higher Deligne conjecture on Hochschild cohomology as in \cite[sec.5.3]{lurie_ha}. Thus, from \cref{prop:framed_ndisk=En}, we know that it is very important to the theorem to work with framed disks since these are the ones that reproduce the $\mathbb{E}_n$-algebras of the higher Deligne conjecture. The proof of the proposition is not easily generalizable to other tangential structures. The associative algebra $\mathsf{Z} (B)$ is the center of $B$ as defined in \cite[def.5.3.1.6]{lurie_ha}, so that even the statement, which implies that $\mathsf{Z}(B)$ is more than associative, relies on the special structure provided by framing.  
\end{remark}

\begin{remark}
    By definition, the center $\mathsf{Z}(B)$ is the universal object that acts on $B$, i.e. all objects that act on $B$ factor through the action of the center $\mathsf{Z}(B)$ on $B$. Keeping this in mind, we see that, informally, \cref{thm:classif_disk_d_under_n*_alg} is saying that the structure of coupling the defect algebra $B$ to the bulk algebra $A$ is by giving $B$ a suitable module structure over $A$. The complication then lies in proving what this suitable module structure is. 
\end{remark}

>>>>

Factorization homology (also known as topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
%
\begin{equation}
    \int_{M} A \in \catC.
\end{equation}
%
The physical interpretation is that given a spacetime $M$ and local observables $A$, $\int_MA$ returns global observables, though typically not all of them.

This implementation, with $M$ relaxed to a stratified manifold and $A$ to an appropriate type of algebra, is sometimes termed `alpha' factorization homology, as opposed to the `beta' version of \cite{ayala2020factorization} that evaluates $(\infty,n)$-categories on variframed stratified $n$-manifolds. In this work, we will be concerned, in this sense, with alpha factorization homology.

Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense. The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}. Later, in \Cref{thm:disk_alg=lcfa}, we will also see how factorization homology serves to construct factorization algebras. The theory of factorization homology in the manner that we will recall here has been developed in \cite{francis2013,af_fhtop, aft_fhstrat}. We will follow the introductory text \cite{af_primer}.

In the following, and from now on, we let $\catC$ be a symmetric monoidal $\infty$-category that is \emph{$\otimes$-presentable} \cite{af_fhtop}, i.e. it satisfies:
%
\begin{enumerate}
    \item $\catC$ is presentable: it admits colimits, and every object is a filtered colimit of compact objects\footnote{For the exact meaning of these terms we refer the reader to \cite[§5.3]{lurie_htt}. For us, it will suffice to give examples of $\infty$-categories that satisfy these requirements.}, and
    \item the monoidal structure distributes over colimits: for all $c \in \catC$, the functor $c \otimes -: \catC \xrightarrow{} \catC$ takes colimit diagrams to colimit diagrams.
\end{enumerate}

@@

\begin{example}
    The following are examples of $\otimes$-presentable categories:
    %
    \begin{enumerate}
        \item chain complexes $\mathscr{C}\mathsf{h}_{\mathbb{k}}$ over a commutative ring $\mathbb{k}$, where equivalences are given by quasi-isomorphism. The symmetric monoidal structure can be both direct sum $\oplus$ or tensor product $\otimes$.
        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Spaces}$ or $\cat$).
    \end{enumerate}
    %
    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most relevant for physical examples which is why it is the target of choice in \cite{cg2016} and \cite{ginot2015}.
\end{example}

@@

We will now recall the $\infty$-category of disk algebras with a chosen tangential structure valued in a symmetric monoidal $\infty$-category. First, recall Segal's category $\mathsf{Fin}_{\ast}$ of finite pointed sets and their maps. By abuse, we write $\mathsf{Fin}_\ast=\mathsf{N}(\mathsf{Fin}_\ast)$ for its nerve. Following \cite{lurie_ha}, we take the objects of $\mathsf{Fin}_{\ast}$ to be $\langle n\rangle=\{\ast,1,\dots,n\}$. For every $i\in\{1,\dots,n\}$ there is a map $\rho^i\colon\langle n\rangle\to\langle 1\rangle$ that sends $i$ to $1$ but is otherwise constant at $\ast\in\langle1\rangle$. A \emph{symmetric monoidal $\infty$-category} is, according to \cite[Definition 2.0.0.7]{lurie_ha}, a cocartesian fibration\footnote{A \emph{cocartesian fibration} (\cite[Definition 01T5]{lurie_kerodon}) $q\colon\mathscr{A}\to\mathscr{B}$ between simplicial sets is one such that every edge $f\colon\mathscr{A}_1$ is \emph{$q$-cocartesian}, that is, any horn of type $\Lambda^n_0\to\mathscr{A}$, $n\geq2$, whose restriction to $\{0<1\}$ is $f$, admits a filler if its projection to $\mathscr{B}$ admits a filler.} $\catC\to\mathsf{Fin}_\ast$ such that the maps the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence $\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}$ for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$. We mostly abbreviate $\catC\to\mathsf{Fin}_\ast$ to $\catC$.

The $\infty$-category $\mathsf{Fun}^{\otimes}(\catC,\mathscr{D})\subset\mathsf{Fun}_{/\mathsf{Fun}_\ast}(\catC,\mathscr{D})$ of \emph{symmetric monoidal functors} is the full sub-$\infty$-category of all the functor $\infty$-category on those functors that preserve cocartesian edges.

@@

\begin{remark}
    The exact specification of the above $\infty$-category is not immediate, but the explanations given in \cite[def.2.0.0.7]{lurie_ha}, \cite[rem.2.1.2.19]{lurie_ha} and \cite[def.2.1.3.7]{lurie_ha} clarify the matter. A succinct explanation is also given around \cite[def.1.11]{aft_fhstrat}. Informally, the objects will be symmetric monoidal functors from $\disk(\bstr)$ to $\catC$. These are given by functors $F:\disk(\bstr) \xrightarrow{} \catC$ together with maps
    %
    \begin{equation}\label{eq:symmon_maps}
        F(U \sqcup V) \xrightarrow{\ \ \simeq \ \ } F(U) \otimes F(V),
    \end{equation}
    %
    and such that the swap in $\disk(\bstr)$, $U \sqcup V \simeq V \sqcup U$, is sent to the swap in $\catC$, $F(U) \otimes F(V) \simeq F(V) \otimes F(U)$, in a way that is compatible with the maps in \eqref{eq:symmon_maps}. A good informal explanation of this and other topics related to disk algebras can be found in the lecture notes \cite{tanaka20}.
\end{remark}

@@

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[sec.5.1]{lurie_ha}. %or alternatively in appendix \Cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent. Through the work of \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
\end{remark}

@@

\begin{remark}
    Because of \Cref{rem:disk_b=disk_bsc}, the above construction works for manifolds with any general $\bstr$-structure, with no further requirements on the constructible bundle $f$.
\end{remark}

@@

The upshot is that, with our setup and assumptions on $\catC$, the guess that the value of factorization homology can be calculated by a colimit is correct and given by the standard expressions for left Kan extensions
%
\begin{equation}
    \int_M A \simeq \mathsf{colim} \left(\disk(\bstr)_{/M} \xrightarrow{} \disk(\bstr) \xrightarrow{A} \catC \right)
\end{equation}
%
in the absolute case, and
%
\begin{equation}
    \int_{N \xhookrightarrow{} M} A \simeq \mathsf{colim} \left((\disk_{/M})_{/(N \xhookrightarrow{} M)} \xrightarrow{} \disk_{/M} \xrightarrow{A} \catC \right)
\end{equation}
%
in the relative case. Namely, the left Kan extension of underlying $\infty$-categories lifts to a symmetric monoidal, in the absolute case, and operadic, in the relative case, left Kan extension. In the relative case, we will almost always abuse notation and write $\int_N A$ instead of $\int_{N \xhookrightarrow{} M} A$, but because of \Cref{lem:double_slice} this is not much of an abuse. Furthermore, factorization homology is also shown to be fully faithful due to this being true for the inclusion $\disk(\bstr) \xrightarrow{} \mfld(\bstr)$, as well as, the relative version with slices.

@@

We want to show that disk algebras with $\mathsf{D}_1^{\partial, *}$-structure, as defined in \Cref{con:d_1^bor_structure}, can be described algebraically. For this we set up two $\infty$-operads $\mathsf{Assoc^{RL}}$ and $\mathsf{O^{RL}}$.

@@

\begin{remark}
    More informally, what the \Cref{con:assocRL} says is that the only multi-morphism domains possible are $\emptyset$, $(A,A,\dots,A)$, $(R,A,\dots,A)$ or $(A,\dots,A, L)$ and that there is one multi-morphism for each permutation of the $A$ entries. This makes it clear that algebras over this $\infty$-operad will be unital, (homotopy) associative algebras, together with a unital left and a unital right module.
\end{remark}

@@

\begin{proposition}\label{prop:disk1bor_over_int=ORL}
    There are equivalences of $\infty$-operads
    %
    \begin{equation}
        \disk[r] (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{\ \ \simeq \ \ } \mathsf{O^{RL}} \quad
    \end{equation}
    %
    that descend to the equivalences of \Cref{prop:disk1bor=assocRL}.
\end{proposition}

\begin{proof}
    As in the proof of \Cref{prop:disk1bor=assocRL} the first equivalence is clear. The idea to keep in mind is that since the boundary of $[-1,1]$ consists of a left point and a right point, there can only be oriented embeddings of disks into $[-1,1]$ with at most one of each of $\left[-1,1 \right)$ and $\left( -1, 1 \right]$. These are then clearly the objects that map to the respective distinguished subsets. Observing the definition of $\mathsf{O^{RL}}$ clearly offers a bijection on morphism spaces since they are by definition order preserving maps, and the embeddings are oriented. It is trivial to check that these maps lie over $\mathsf{Fin}_*$ and that they send active morphisms to active morphisms completing the proof.
\end{proof}

@@

\begin{proof}
    The only thing to show is the middle equivalence. This follows from \Cref{lem:disk/M_to_disk}, which we will introduce later. 
\end{proof}

\begin{remark}\label{rem:fin_equiv_natural}
    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
    %
    \begin{equation}\label{eq:fin_equivs_obj}
        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
    \end{equation}
    %
    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist. We remark here that these equivalences are actually even natural in $G$. To explain this, we first notice that the equivalences in \Cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
    %
    \begin{equation}\label{eq:fin_equivs_cat}
        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
    \end{equation}
    %
    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one. Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the slice construction is functorial, which, after restricting, defines the functors
    %
    \begin{align}
        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
    \end{align}
    %
    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$. We can now state that by naturality in $G$ we mean that the functors of \Cref{eq:fin_equivs_cat} assemble into an equivalence of functors   
    %
    \begin{equation}
        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
    \end{equation}
    %
    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \Cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
\end{remark}

@@

    Since the equivalences above come from an argument about finality, \Cref{rem:fin_equiv_natural} tells us that they are actually even natural in the algebra variable $(R, A, L)$, so that the equivalence lifts to the level of functors.
\end{proof}

@@

The construction of \Cref{lem:f^-1} gives a functor which allows us to change the stratified manifold over which we work. This brings about the important operation of pushforward:

@@

\begin{remark}\label{rem:fh_pushforward_functorial}
    As was the case with the bar construction the equivalence of \Cref{thm:fh_pushforward}, comes about through an argument about a final functor, this means that, through \Cref{rem:fin_equiv_natural} there is even an equivalence between functors
    %
    \begin{equation}
        \int_M -, \int_N f_* - : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \catC.
    \end{equation}
\end{remark}

@@

\begin{proof}
    The definition comes with a claim that the canonical morphism in $\catC$ exists. This we need to show. The data of a collar-gluing $f: M \xrightarrow{} [-1,1]$ allows us to pushforward $F$ to
    %
    \begin{equation}
        f_*F: \disk (\mathsf{D}_1^{\partial, *})_{/[-1,1]} \xrightarrow{f^{-1}} \mfld(\bstr)_{/M} \xrightarrow{} \mfld(\bstr) \xrightarrow{F} \catC.
    \end{equation}
    %
    By \Cref{prop:disk1bor=assocRL} we know that this data defines an $\mathsf{Assoc^{RL}}$-algebra in $\catC$ whose right module, algebra and left module are exactly $F(M_-)$, $F(M_0 \times \mathbb{R})$ and $F(M_+)$. Further using \Cref{prop:barconst=intinterval} we have
    %
    \begin{equation}
        F(M_-) \bigotimes\limits_{f(M_0 \times \mathbb{R})}  F(M_+)\simeq \int_{[-1,1]} f_* F \xrightarrow{\quad} F (f^{-1}[-1,1]) = F(M),
    \end{equation}
    %
    where the morphism is given by the fact that factorization homology is a colimit.
\end{proof}

@@

All of the above statements about factorization homology and disk algebras are quite general, and they do not say anything specific about a stratified structure, if there is one. Namely, had we stuck to smooth manifolds (possibly with boundary) we could have made similar statements. In this section we describe a result that clearly uses the stratified structure, and quantifies some additional information it can encode. It is a classification statement about disk algebras whose structure $\mathsf{D}_{d \subset n}^*$ is provided by \Cref{def:framed_d_under_n_structure}. %We will, in a roundabout way, recover this result in \Cref{ch:classif_defect_mfld}, but here we state it in the original form.

@@

\begin{remark}
    The above theorem is a slight generalization of, and heavily relies on, the proof of the higher Deligne conjecture on Hochschild cohomology as in \cite[sec.5.3]{lurie_ha}. Thus, from \Cref{prop:framed_ndisk=En}, we know that it is very important to the theorem to work with framed disks since these are the ones that reproduce the $\mathbb{E}_n$-algebras of the higher Deligne conjecture. The proof of the proposition is not easily generalizable to other tangential structures. The associative algebra $\mathsf{Z} (B)$ is the center of $B$ as defined in \cite[def.5.3.1.6]{lurie_ha}, so that even the statement, which implies that $\mathsf{Z}(B)$ is more than associative, relies on the special structure provided by framing.  
\end{remark}

\begin{remark}
    By definition, the center $\mathsf{Z}(B)$ is the universal object that acts on $B$, i.e. all objects that act on $B$ factor through the action of the center $\mathsf{Z}(B)$ on $B$. Keeping this in mind, we see that, informally, \Cref{thm:classif_disk_d_under_n*_alg} is saying that the structure of coupling the defect algebra $B$ to the bulk algebra $A$ is by giving $B$ a suitable module structure over $A$. The complication then lies in proving what this suitable module structure is. 
\end{remark}
